Browsing the Web of Factual Claims

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
First draft of related work now completed

Many web clipping systems are also web annotation systems. Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people. Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents. More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages.

@@

In our existing web, links are created primarily by the authors of a document, rather than the readers. In Vannevir Bush's seminar MEMEX article~\cite{memex} he proposed a different architecture, in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}.

\subsection{Sensemaking Tools}

\cite{scenthighlights}\cite{scenttrails}
\cite{quotations}, \cite{quotationdl} Overall aim is to identify and connect ideas. Do quotation matching as a partial solution.

\cite{scenthighlights}

\cite{ideanavigation}, \cite{citesense}

@@

The 
\cite{Korb97acognitive}
\cite{toulmin}
\cite{carneades}
\cite{conceptmap}
\cite{argmas}

Memex
Vannevar 
Bush's vision of Memex. Bush popularized the idea that 
people can collaboratively organize and share knowledge: 
``Wholly new forms of encyclopedias will appear, ready-made 
with a mesh of associative trails running through them...'' 
[5]. In many ways the vision has come to pass with large 
amounts of hyper-linked information in the World Wide 
Web, digital libraries, and online encyclopedias. However, 
researchers continue to point out that people, especially 
those lacking domain expertise, struggle to navigate infor- 
mation spaces.

\subsection{Semantic Linking}

\subsection{Social Bookmarking}

Shadows

\subsection{Automated Reasoning}

Case-Based reasoning
Sensemaking

>>>>

Many web clipping systems are also web annotation systems. Web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, DrawHere~\cite{drawhere}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add annotations to existing web pages and view annotations written by other people. Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents. More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages. Perhaps the tool most similar to Think Link is SpinSpotter~\cite{spinspotter}, a tool that allows users to mark up newspaper articles to identify spin and factual inaccuracies.

@@

In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Similar approaches have been taken by other hypertext systems including EQUIRE~\cite{enquire} and Everything2~\cite{everything2}. Think Link very much follows in this philosophy, the key difference being that Think Link structures its connections between documents using a graph of factual claims.

\subsection{Browsing Ideas}

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

%\cite{citesense}

@@

Argumentation Theory is a whole field in itself~\cite{argumentation,argmas} and much has been written about ways that one can represent arguments using a graph of connected claims. Popular argument representations include the Toulmin Model~\cite{toulmin}, and the Carneades Model~\cite{carneades}. Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model as they typically want to represent more of the logic of the argument, and perhaps even be able to do reasoning. Early versions of Think Link used a more complex model and we cut things down in order to make it easier for users to assemble claim graphs.

One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.

%\subsection{Automated Reasoning}
%
%Case-Based reasoning
%Sensemaking
